---
title: "Cleaning Sensor Locations"
author: "Hayley Garment"
date: "6/17/2020"
output: html_document
---

In this file:
1. Matching AirVisual Serial Codes with Station Names by LonLat
2. Matching AirVisual Serial Codes with Station Names by Proximity

Output: 
1. data/stations_serial_num.rds - station code, lat, lon

Ultimately, these two sets are not the same. So just use the Public Lab stations without names.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(tmap)
library(broom)
library(rgdal)
```


**READING DATA**
```{r}
station_names_lonlat <- read.csv('raw_data/stations_name_lonlat.csv')
stations_serialnum_lonlat <- read.csv('raw_data/air_visual_data/stations_serial_code_lonlat.csv')
```

*A. Get standard lon and lat from serial coded stations*
```{r}
stations_serialnum_lonlat <- stations_serialnum_lonlat %>% mutate(coor = as.character(Coordinate))

# fix up typo
stations_serialnum_lonlat <- stations_serialnum_lonlat %>%
  mutate(coor = ifelse(Serial.Number == 'LUAKYUG', '47.912120, 106.953814', coor))

# put lon lat into separate columns
stations_serialnum_lonlat <- stations_serialnum_lonlat %>%
  separate(coor, into=c('lat', 'lon'), sep=', ', remove=TRUE) %>%
  select(-Share.Code) %>%
  rename(serial_number = Serial.Number)

stations_serialnum_lonlat$lat <- as.double(stations_serialnum_lonlat$lat)
stations_serialnum_lonlat$lon <- as.double(stations_serialnum_lonlat$lon)

saveRDS(stations_serialnum_lonlat, 'data/stations_serial_num.rds')
```

**1. Matching AirVisual Serial Codes with Station Names by LonLat**
*Joining based on lon lat only gets a perfect match for 16 of 23 stations.*
```{r}
station_names_lonlat
stations_serialnum_lonlat

inner_join(x=stations_serialnum_lonlat, y=station_names_lonlat, by=c('lon', 'lat') )
```


**2. Matching AirVisual Serial Codes with Station Names by Proximity**
*Try to map the stations and see which are comparable*
```{r}
sf_airvisual <- st_as_sf(station_names_lonlat, 
                         coords = c("lon", "lat"), 
                         crs = 4326) %>%
                st_transform(3414)

sf_publiclab <- st_as_sf(stations_serialnum_lonlat, 
                         coords = c("lon", "lat"), 
                         crs = 4326) %>%
                st_transform(3414)
```

*It turns out that the stations only overlap for 16 stations, Air Visual is reporting more stations, possibly govt stations.*
*Public lab has some sensors that are NOT on the air visual API?*
*Use Public Lab's for kriging, and for the LUR can use govt data as possible test*
```{r}
tmap_mode("view")
  
# Plot
tm_shape(sf_airvisual) + 
  tm_dots(col='blue') +
  tm_shape(sf_publiclab) +
  tm_dots(col='red')

```