---
title: "Generate Frame Input Data"
author: "Hayley Garment"
date: "7/13/2020"
output: html_document
---

In this file:
1. Calculate daily average at each sensor where there is data
2. Add in predictions to daily avg table
3. Calculate 7 day average for each day/sensor
4. Extract frame input data by sampling every 4 days

Output:

1. 'data/no_gap_daily_avgs.rds' - either observed or predicted value every day at every station between feb 14th 2019 and may 1st 20120

2. 'data/moving_daily_avg_every_4th_day.rds' - 7 day average, sampled every 4th day

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
library(geostatsp)
library(gstat)
library(pracma) # movavg
```

*Load station locations*
```{r}
stations <- read_rds('data/stations_serial_num.rds') %>% rename(station_serial = serial_number)
#stations_sf <- st_as_sf(stations, coords = c("lon", "lat"), crs = 4326) 
#tm_shape(stations_sf) + tm_dots()
```

*Load sensor data*
```{r}
sensor_data <- readRDS('data/sensor_data_tidy.rds') %>% filter(station_serial != 'SLSVLW4')
```

*Load prediction data*
```{r}
predictions <- readRDS('data/all_monthly_predictions.rds')
```

**1. Calculate daily average at each sensor**
*Get daily average per sensor, so long as sensor has 24 readings. Only between Feb 15th 2019 and April 30th 2020*
```{r}
daily_avgs <- sensor_data %>% 
  mutate(date = date(datetime)) %>% 
  group_by(station_serial, date) %>% 
  summarise(avg_pm25 = mean(pm25_ug), num_readings = n()) %>% 
  ungroup()

#check
#daily_avgs %>% count() #8632
#daily_avgs %>% filter(num_readings >= 23) %>% count() #6832

daily_avgs <- daily_avgs %>% filter(num_readings >= 23)
daily_avgs <- daily_avgs %>% filter(date >= '2019-02-14' & date < '2020-05-01') %>% arrange(date)
```

LIST STATION SERIALS
```{r}
daily_avgs %>% distinct(station_serial)
```

*plot without avg*
```{r}
daily_avgs %>% ggplot(aes(x=date, y=avg_pm25, col=station_serial)) + geom_line()
```


*Explore where the gaps are for each sensor*
```{r}
station = 'RR9M4V9'

daily_avgs %>% filter(station_serial == station) %>% 
  ggplot(aes(x=date, y = avg_pm25)) + geom_point()

predictions %>% filter(station_serial == station) %>% ggplot(aes(x=date, y=predicted)) + geom_line()
```

**2. Fill in gaps with predictions**
```{r}
# add in prediction for every day using LUR prediction data
predictions <- predictions %>% 
  mutate(year = year(date), month = month(date))
```

**smooth predictions a bit**

*Get Dates Table*
```{r}
dates <- daily_avgs %>% distinct(date) %>% arrange(date) # 442 days
dates <- dates %>% mutate(year = year(date), month = month(date))

days_per_month <- dates %>% group_by(year, month) %>% 
  summarize(n_days = n()) %>% 
  ungroup()
```

*Calculate duration and change in avg per month, then smooth predictions*
```{r}
# get lead and lag to calculate slope
lead_lag_predictions <- predictions %>% 
  arrange(date) %>% 
  group_by(station_serial) %>% 
  mutate(prev_month = lag(predicted, order_by=date),
         next_month = lead(predicted, order_by=date)) %>% 
  ungroup() %>% 
  mutate(prev_month = if_else(is.na(prev_month), predicted, prev_month), 
         next_month = if_else(is.na(next_month), predicted, next_month)) 

# take avg between two months as endpoints
lead_lag_predictions <- lead_lag_predictions %>% 
  mutate(prev_val = (predicted + prev_month)/2,
         next_val = (predicted + next_month)/2) 

lead_lag_predictions <- lead_lag_predictions %>% left_join(days_per_month)
lead_lag_predictions <- lead_lag_predictions %>% dplyr::select(-date)

dates_with_lead_lag_predictions <- left_join(dates, lead_lag_predictions)

dates_with_lead_lag_predictions <- dates_with_lead_lag_predictions %>% 
  mutate(day = if_else(year == 2019 & month == 2, day(date) - 14, day(date) - 1))
  
dates_with_smooth_predictions <- dates_with_lead_lag_predictions %>% mutate(predicted_smooth = prev_val + (day * (next_val - prev_val) / n_days ))


dates_with_smooth_predictions <- dates_with_smooth_predictions %>% dplyr::select(date, station_serial, predicted, predicted_smooth)
```


```{r}
station = 'KT4KJ47'

dates_with_smooth_predictions %>% filter(station_serial == station) %>% 
  ggplot(aes(x=date, y = predicted_smooth)) + geom_point()
```



```{r}
# join with daily_avgs and see where there are gaps :P
actual_predicted_by_date <- left_join(dates_with_smooth_predictions, daily_avgs)

no_gap_daily_avg <- actual_predicted_by_date %>% mutate(avg_pm25_fill = if_else(is.na(avg_pm25), predicted_smooth, avg_pm25))

#saveRDS(no_gap_daily_avg, 'data/no_gap_daily_avgs.rds')
```




**3. Calculate 7 day average for each day/sensor**
```{r}
no_gap_daily_mov_avg <- no_gap_daily_avg %>% 
  group_by(station_serial) %>% 
  arrange(date) %>% 
  mutate(mov_avg_pm25 = movavg(avg_pm25_fill, 7, "s")) %>% 
  ungroup()

every_4th_day <- no_gap_daily_mov_avg %>% group_by(station_serial) %>% 
  filter(row_number() %% 4 == 1) %>% 
  ungroup()

#saveRDS(every_4th_day, 'data/moving_daily_avg_every_4th_day.rds')

every_4th_day %>% filter(station_serial == 'GCWJPX9')
```

Investigate :) Looks nice!
```{r}
station = 'GCWJPX9'
daily_avgs %>% distinct(station_serial)

daily_avgs %>% filter(station_serial == station) %>% 
  ggplot(aes(x=date, y = avg_pm25)) + geom_point()

no_gap_daily_avg %>% filter(station_serial == station) %>% 
  ggplot(aes(x=date, y = avg_pm25_fill)) + geom_point()

no_gap_daily_mov_avg %>% filter(station_serial == station) %>% 
  ggplot(aes(x=date, y = mov_avg_pm25)) + geom_point()
```



EXTRA WORK TO GET END OF FEB AVGS
*Figuring out the averages for just the last weeks of February - starting 14th feb*
```{r}
#february_daily <- sensor_data %>% 
  mutate(month = month(datetime), year = year(datetime), week = floor(day(datetime)/7)) %>%
  filter(month == 2 & year == 2019) %>% 
  group_by(station_serial, week) %>% 
  summarise(avg_pm25 = mean(pm25_ug), num_readings = n()) %>% 
  ungroup()

#february_daily %>% filter(num_readings > 130) %>% group_by(week) %>% 
  summarize(num_stations = n()) %>% ungroup()

end_of_feb_avgs <- sensor_data %>% 
  mutate(month = month(datetime), year = year(datetime), week = floor(day(datetime)/7)) %>%
  filter(month == 2 & year == 2019 & week > 1) %>% 
  group_by(station_serial) %>% 
  summarise(avg_pm25 = mean(pm25_ug), num_readings = n()) %>% 
  ungroup()

end_of_feb_avgs <- end_of_feb_avgs %>% filter(num_readings > 350) %>% mutate(datetime = 5) %>% rename(monthly_avg_pm25 = avg_pm25) %>% left_join(stations)

saveRDS(end_of_feb_avgs, 'data/monthly_avgs/month_of_end_feb_2019.rds')

```

