---
title: "Computing the regression with more predictor values"
author: "Hayley Garment"
date: "7/2/2020"
output: html_document
---

In this file:
1. Join predictor and indpendent variables at each station
2. Regression

Output:


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
```

*Load predictor variables at each station*
```{r}
predictor_vals <- read.csv('data/sensor_locations_predictor_values.csv') %>% 
  rename(station_serial = serial_num) %>% dplyr::select(-FID, -lat, -lon)
```


*Load independent variable at each station -pm2.5 avg
**Sample**
```{r}
jan_2020_avg <- readRDS('data/monthly_avgs/month_of_2019-06-01.rds') %>% dplyr::select(-datetime)

jan_2020_avg
```

*look on map*
```{r}
tmap_mode("view")
jan_2020_geo <- st_as_sf(jan_2020_avg, coords = c("lon", "lat"), crs = 4326) 
tm_shape(jan_2020_geo) + tm_dots(col='monthly_avg_pm25')
```


**1. Join predictor and indpendent variables at each station**
```{r}
jan_2020_data <- left_join(jan_2020_avg, predictor_vals)
```

```{r}
ggplot(jan_2020_data, aes(x=major_road_01, y=monthly_avg_pm25)) + geom_point()
ggplot(jan_2020_data, aes(x=major_road_005, y=monthly_avg_pm25)) + geom_point()
ggplot(jan_2020_data, aes(x=res_road_01, y=monthly_avg_pm25)) + geom_point()
ggplot(jan_2020_data, aes(x=res_road_005, y=monthly_avg_pm25)) + geom_point()
```


```{r}
ggplot(jan_2020_data, aes(x=stove_conc_01, y=monthly_avg_pm25)) + geom_point()
ggplot(jan_2020_data, aes(x=stove_conc_005, y=monthly_avg_pm25)) + geom_point()
ggplot(jan_2020_data, aes(x=PathDis_ci, y=monthly_avg_pm25)) + geom_point()
```


**2. Regression**

*major road density - neither particuarly promising*
```{r}
ols <- lm(monthly_avg_pm25 ~ major_road_01 + major_road_005, jan_2020_data)

ols %>% summary()

tidy(ols)
```
*residential road density - 005 is promising*
```{r}
ols <- lm(monthly_avg_pm25 ~ res_road_01 + res_road_005, jan_2020_data)

ols %>% summary()

tidy(ols)
```


*stove concentration - 005 promising *
```{r}
ols <- lm(monthly_avg_pm25 ~ stove_conc_01 + stove_conc_005, jan_2020_data)

ols %>% summary()

tidy(ols)
```
*path distance to city - ok not terrible! *
```{r}
ols <- lm(monthly_avg_pm25 ~ PathDis_ci, jan_2020_data)

ols %>% summary()

tidy(ols)
```


*Testing out variables together*
```{r}
ols <- lm(monthly_avg_pm25 ~ PathDis_ci + res_road_005 + stove_conc_005, jan_2020_data)

ols %>% summary()

tidy(ols)
```
```{r}
jan_2020_data_with_predictions <- augment(ols, data = jan_2020_data)

# plot residuals
jan_2020_data_with_predictions %>% 
  ggplot(aes(x = .resid)) +
  geom_histogram(bins = 50) +
  geom_vline(xintercept=0) +
  ggtitle('Jan 2020')

summary(ols)
```


```{r}
jan_2020_predictions_geo <- st_as_sf(jan_2020_data_with_predictions, coords = c("lon", "lat"), crs = 4326) 
tm_shape(jan_2020_predictions_geo) + tm_dots(col='monthly_avg_pm25')
tm_shape(jan_2020_predictions_geo) + tm_dots(col='.fitted')
tm_shape(jan_2020_predictions_geo) + tm_dots(col='.resid')
```

