---
title: "Computing Basic Rasters Using Data Fusion for Each Frame"
author: "Hayley Garment"
date: "7/14/2020"
output: html_document
---

In this file:
1. For each frame data generate residuals from monthly LUR
2. 

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
library(geostatsp)
library(gstat)
library(stars)
```

**1. For each frame data generate residuals from monthly LUR**
*Load in the weekly avg dataframe*
```{r}
mov_weekly_avgs <- readRDS('data/moving_daily_avg_every_4th_day.rds')
mov_weekly_avgs <- mov_weekly_avgs %>% 
  dplyr::select(date, station_serial, mov_avg_pm25) %>% 
  mutate(year = year(date), month = month(date))
```

*Load in monthly predictions*
```{r}
lur_predictions <- readRDS('data/all_monthly_predictions.rds')
lur_predictions <- lur_predictions %>%
  mutate(year = year(date), month = month(date)) %>% 
  dplyr::select(-date) %>% 
  rename(lur_predicted = predicted)
```

*Add in lur prediction to the mov_avg to get the residuals*
```{r}
mov_avg_with_residuals <- mov_weekly_avgs %>% left_join(lur_predictions) %>% 
  mutate(residual = mov_avg_pm25 - lur_predicted)
```

**2.**
*make data spatial so can do idw*
```{r}
station_serials <- readRDS('data/stations_serial_num.rds')
station_serials <- station_serials %>% rename(station_serial = serial_number)

residuals_lonlat <- left_join(mov_avg_with_residuals, station_serials, by="station_serial") %>% dplyr::select(-Coordinate)
```

*get raster layer output data*
```{r}
# using one of my tifs as example
sampleLUR <- raster('lurs/2020_02_LUR1.tif')
sampleLUR2 <- raster('lurs/2019_02_LUR1.tif')

extent <- extent(sampleLUR)
extent(sampleLUR2)



extent(croppedLURExtent)

origin(sampleLUR)

```

*IDW*
```{r}
band_breaks <- c(-Inf, 15, 1,
                 15, 25, 2,
                 25, 50, 3,
                 50, 75, 4,
                 75, 100, 5,
                 100, 125, 6,
                 125, 150, 7,
                 150, 175, 8,
                 175, 200, 9,
                 200, 225, 10,
                 225, 250, 11,
                 250, 300, 12,
                 300, 350, 13,
                 350, Inf, 14)

# how to reclassify the raster
rclassify_mat <- matrix(band_breaks, ncol=3, byrow=TRUE)

# smaller LUR extent
sampleLUR <- raster('lurs/2020_02_LUR1.tif')
extent <- extent(sampleLUR)

generateRasterFrame <- function(frame_date, month_lur) {
  #0 Get output grid based on lur, fix month_lur extent
  
  cropped_month_lur <- crop(month_lur, extent)
  month_lur <- resample(cropped_month_lur, sampleLUR)
  
  # Initialize the new raster layer
  output_grid <- raster(extent)
  
  # Set the resolution to be that of example
  res(output_grid) <- res(month_lur)
  output_grid[] <- 0
  extent(output_grid) <- extent
  extent(month_lur) <- extent
  output_grid <- as(output_grid, 'SpatialGridDataFrame')
  
  
  # 1. grab data + add coors and crs
  frame_data <- residuals_lonlat %>% filter(date == date(frame_date))
  coordinates(frame_data) <- c("lon", "lat")
  crs(frame_data) = crs(output_grid)
  
  #2. calculate the idw raster and add it to the LUR
  frame_idw <- gstat::idw(formula=residual~1, locations=frame_data, newdata=output_grid, idp=2)
  raster_idw <- raster(frame_idw)
  raster_frame <- month_lur + raster_idw
  
  grid_finer <- raster::disaggregate(raster_frame, fact = 10)
  #3. resample to be finer
  resample_finer <- resample(raster_frame, grid_finer, method="bilinear")
  
  # reclassify to integer bands
  final_banded_raster <- reclassify(resample_finer, rclassify_mat, include.lowest=TRUE)
  final_banded_raster
}

```

*Loop through dates and generate rasters*
```{r}
frame_dates <- residuals_lonlat %>% 
  distinct(date) %>% 
  mutate(year_and_month = str_replace_all(str_sub(date, 1, 8), '-', '_'))

for(i in 1:30) { #nrow(frame_dates)
  frame_date <- frame_dates$date[i]
  
  # get the appropriate LUR for that month
  frame_year_and_month <- frame_dates$year_and_month[i]
  lur_filename <- paste0('lurs/', frame_year_and_month, 'LUR1.tif', sep='')
  LUR <- raster(lur_filename)
  
  raster_frame <- generateRasterFrame(frame_date, LUR)
  filename <- paste0('frames/air_quality_bands_', frame_date, '.tif', sep='')
  #tm_shape(raster_frame) + tm_raster(alpha=0.5, palette = "RdPu", n = 9)

  writeRaster(raster_frame, filename, format = "GTiff")
}
```



*View*
```{r}
color_breaks <- c(0, 25, 50, 100, 150, 200, 250, 300)
tmap_mode("view")
tm_shape(sample_with_idw) + tm_raster(alpha=0.5, palette = "RdPu", n = 9, breaks = color_breaks)
tm_shape(raster_idw) + tm_raster(alpha=0.5, palette = "RdPu", n = 9, breaks = color_breaks)

```

*TEST RESAMPLE*
```{r}
res(sample_with_idw)
sample_finer <- raster::disaggregate(sample_with_idw, fact = 10)
res(sample_finer)

resample_finer <- resample(sample_with_idw, sample_finer, method="bilinear")

writeRaster(sample_with_idw_cut_bands, "sample_frame_raster_bands.tif", format = "GTiff")
```
