---
title: "Extracting Raster Values at Sensor Points"
author: "Hayley Garment"
date: "6/24/2020"
output: html_document
---

In this file:

1. Create raster stack
2. Extract values in rasters to sensos/station points

Output:

1. data/lur_predictor_vals_per_station.rds - for each station, value of each predictor

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
```

*Load sensor points*
```{r}
station_locations <- readRDS('data/stations_serial_num.rds')
```


*Load raster data*
```{r}
stove_005 <- raster('data/lur_rasters/stove_concentration_point005.tif') #these are not right
stove_01 <- raster('data/lur_rasters/stove_concentration_point01.tif')

#this has the correct extent..
topo <- raster('raw_data/ub_topography.tif')

#plot(stove_005)

```

*Create spatial points from station lon lats*
```{r}
station_lonlat <- station_locations[,c(4,3)]
station_points <- SpatialPoints(coords = station_lonlat)
#class(points)
```

**1. Create raster stack**

*Make data 'stackable'*
```{r}
#check extents, they're slightly different, though I tried to use the same one in argGIS
extent(stove_005)
extent(stove_01)
extent(topo)
```

```{r}
# crop the extents
generic_extent <- extent(stove_01)

extent(stove_005) <- generic_extent
extent(topo) <- generic_extent
```

```{r}
# resample to the resolution of the finest layer, topography 
stove_01_resampled <- resample(stove_01, topo, method='bilinear')
stove_005_resampled <- resample(stove_005, topo, method='bilinear')

plot(stove_005)
plot(stove_005_resampled)
# hmm
```

*Put the raster stack together*
```{r}
rasterStack <- stack(stove_005_resampled, stove_01_resampled, topo)
```



**2. Extract values in rasters to sensos/station points**
```{r}
data_per_point <- extract(rasterStack, station_points)

station_lur_data <- cbind(station_locations, as.data.frame(data_per_point))

#saveRDS(station_lur_data, 'data/lur_predictor_vals_per_station.rds')
```
