---
title: "Computing Final Summer LURs"
author: "Hayley Garment"
date: "7/13/2020"
output: html_document
---

In this file:
1. Computing LUR for each Summer Month

Output:

File 'data/all_monthly_predictions.rds' with summer month predictions and previous winter predictions

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
```

*Load predictor variables at each station and station locations*
```{r}
predictor_vals <- read.csv('data/sensor_locations_predictor_values_additional_vars.csv') %>% 
  rename(station_serial = serial_num) %>% dplyr::select(-FID, -lat, -lon) %>% filter(station_serial != 'SLSVLW4')

predictor_vals <- predictor_vals %>% mutate(high_growth = if_else(pop_change > 1, TRUE, FALSE))

stations <- read_rds('data/stations_serial_num.rds') %>% rename(station_serial = serial_number)
```


**1. Computing LUR for each Summer Month**

FUNCTION TO GET DEPENDENT AND INDEPENDENT VARS
```{r}
color_breaks <- c(0, 5, 10, 15, 25, 45, 85, 100)

get_monthly_dataframe <- function(filename) {
  monthly_avg <- readRDS(filename) %>% dplyr::select(-datetime) %>% filter(station_serial != 'SLSVLW4')
  
  # join with predictor vals and create calculated terms
  month_data <- left_join(monthly_avg, predictor_vals)
  month_data <- month_data %>% mutate(lnPM25 = log(monthly_avg_pm25))
  
  month_data
}

view_map <- function(filename) {
  monthly_avg <- readRDS(filename) %>% dplyr::select(-datetime) %>% filter(station_serial != 'SLSVLW4')
  tmap_mode("view")
  monthly_geo <- st_as_sf(monthly_avg, coords = c("lon", "lat"), crs = 4326) 
  tm_shape(monthly_geo) + tm_dots(col='monthly_avg_pm25', palette = "RdPu", n = 9, breaks = color_breaks)
}

show_predictor_table <- function(monthly_dataframe) {
  predictors <- monthly_dataframe %>% 
    dplyr::select(-lon, -lat, -station_serial, -monthly_avg_pm25 , -district) %>%
    colnames()
  
  rsq_no_inractn <- list()
  rsq_with_inractn <- list()
  
  for(i in 1:length(predictors)) {
    predictor <- predictors[i]
    model <- lm(monthly_avg_pm25 ~ get(predictor), monthly_dataframe)
    r_squared <- summary(model)$adj.r.squared
    rsq_no_inractn[[i]] <- r_squared
    
    model <- lm(monthly_avg_pm25 ~ get(predictor):high_growth, monthly_dataframe)
    r_squared <- summary(model)$adj.r.squared
    rsq_with_inractn[[i]] <- r_squared
  }
  
  cbind(predictors, rsq_no_inractn, rsq_with_inractn)
}

#Given OLS, make predictions at each station
ln_get_predictions_at_all_stations <- function(ln_ols) {
  month_data_with_predictions <- augment(ln_ols, newdata = predictor_vals)
  month_data_with_predictions <- month_data_with_predictions %>% mutate(predicted = exp(.fitted))
  month_data_with_predictions
}

get_predictions_at_all_stations <- function(ols) {
  month_data_with_predictions <- augment(ols, newdata = predictor_vals)
  month_data_with_predictions <- month_data_with_predictions %>% mutate(predicted = .fitted)
  month_data_with_predictions
}

#Show Predcitions on Map
show_prediction_map <- function(predictions) {
  predictions_with_lonlat <- left_join(predictions, stations)
  predictions_geo <- st_as_sf(predictions_with_lonlat, coords = c("lon", "lat"), crs = 4326)
  predictions_geo %>% tm_shape() + tm_dots(col='predicted', palette = "RdPu", n = 9, breaks = color_breaks)
}

```


Step 1: Look at Predictors
```{r}
month_in_question <- '2019-02-01'
month_data_file <- paste0('data/monthly_avgs/month_of_', month_in_question, '.rds', sep='')
dataframe <- get_monthly_dataframe(month_data_file)
show_predictor_table(dataframe)
```

Step 1: Try out a LUR
```{r}
ln_ols <- lm(lnPM25 ~ res_road_005, dataframe)
tidy(ln_ols)
summary(ln_ols)$adj.r.squared
```

```{r}
ols <- lm(monthly_avg_pm25 ~ res_road_005 + ub_pop_2019_1km:high_growth, dataframe)
tidy(ols)
summary(ols)$adj.r.squared
```

Step 3: Verify it looks OK on the map
```{r}
predictions_at_stations <- ln_get_predictions_at_all_stations(ln_ols)
#OR
#predictions_at_stations <- get_predictions_at_all_stations(ols)
view_map(month_data_file)
show_prediction_map(predictions_at_stations)
```

Step 4: Save the info!
RECORD TO AIRTABLE
```{r}
selected_ols <- ln_ols
#OR
#selected_ols <- ols

paste(month_in_question)
selected_ols$coefficients
summary(selected_ols)$adj.r.squared
```

SAVE PREDICTIONS - RUN ONLY ONCE!
```{r}
current_month_predictions <- predictions_at_stations %>% select(station_serial, predicted) %>% mutate(date=date(month_in_question))
#add predictions to existing table

saveRDS(current_month_predictions, paste0('data/monthly_predictions/month_of_', month_in_question, '.rds', sep=''))

#first time only
#all_predictions <- current_month_predictions

#except for first set of predictions
all_predictions <- readRDS('data/all_monthly_predictions.rds')
all_predictions <- rbind(all_predictions, current_month_predictions)

saveRDS(all_predictions, 'data/all_monthly_predictions.rds')
```
