---
title: "COMPUTE_4.5_CombinedLUR"
author: "Hayley Garment"
date: "7/7/2020"
output: html_document
---

In this file:
1. Join predictor and indpendent variables at each station
2. Regression

Output:


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
```

*Load predictor variables at each station*
```{r}
predictor_vals <- read.csv('data/sensor_locations_predictor_values_additional_vars.csv') %>% 
  rename(station_serial = serial_num) %>% dplyr::select(-FID, -lat, -lon)
```


*Load independent variable at each station -pm2.5 avg
**Sample**
```{r}
monthly_avg <- readRDS('data/sensor_means_by_month_over_650_readings.rds') %>% dplyr::select(-datetime, -num_readings) %>% filter(station_serial != 'SLSVLW4')
```

*load temperatures for each year and month*
```{r}
monthly_temps <- read_csv('raw_data/ub_monthly_avg_temp.csv')

monthly_avg_and_temps <- left_join(monthly_avg, monthly_temps, by=c('year', 'month'))
```


**1. Join predictor and indpendent variables at each station**
```{r}
month_data <- left_join(monthly_avg_and_temps, predictor_vals)

#month_data
```

**2. Regression**


```{r}
month_data %>% colnames()

predictors <- month_data %>% dplyr::select(-month, -year, -station_serial, -monthly_avg_pm25 , -district) %>% colnames()
```

Look at the individual r squared values for each predictor - bad of course
```{r}
predictor_rsquared <- list()

for(i in 1:length(predictors)) {
  predictor <- predictors[i]
  model <- lm(monthly_avg_pm25 ~ get(predictor), month_data)
  r_squared <- summary(model)$adj.r.squared
  
  predictor_rsquared[[i]] <- r_squared
}

cbind(predictors, predictor_rsquared)

```

Look at possible interaction terms, temp and population change
```{r}
month_data <- month_data %>% mutate(is_winter = avg_temp_c <= 0) %>% mutate(high_growth = if_else(pop_change > 1, TRUE, FALSE))
```

*checking interaction with winter*
```{r}
predictor_rsquared <- list()

for(i in 1:length(predictors)) {
  predictor <- predictors[i]
  model <- lm(monthly_avg_pm25 ~ get(predictor):is_winter, month_data)
  r_squared <- summary(model)$adj.r.squared
  
  predictor_rsquared[[i]] <- r_squared
}

cbind(predictors, predictor_rsquared)
```

COMBINED MODEL FOR MONTHLY AVG
*Testing out variables together*
*0.49: monthly_avg_pm25 ~ PathDis_ci:is_winter + stove_kernel_density_radius_01:is_winter:high_growth +  ub_pop_2019_1km + res_road_01:is_winter:high_growth*

*0.50: monthly_avg_pm25 ~ PathDis_ci:is_winter + stove_kernel_density_radius_01:is_winter:high_growth +  ub_pop_2019_1km + res_road_01:is_winter:high_growth + ub_topogra:is_winter*


```{r}
ols <- lm(monthly_avg_pm25 ~ PathDis_ci:is_winter + stove_kernel_density_radius_007:is_winter:high_growth +  ub_pop_2019_1km + res_road_01:is_winter:high_growth + ub_topogra:is_winter, month_data)

ols %>% summary()

tidy(ols)
```


Divide by is winter or isn't and look at rsquared for each
```{r}
winter_data <- month_data %>% filter(is_winter)
nonwinter_data <-  month_data %>% filter(!is_winter)
```


```{r}
winter_r <- list()
nonwinter_r <- list()
for(i in 1:length(predictors)) {
  predictor <- predictors[i]
  winter_model <- lm(monthly_avg_pm25 ~ get(predictor), winter_data)
  winter_r_squared <- summary(winter_model)$adj.r.squared
  
  nonwinter_model <- lm(monthly_avg_pm25 ~ get(predictor), nonwinter_data)
  nonwinter_r_squared <- summary(nonwinter_model)$adj.r.squared
  
  winter_r[[i]] <- winter_r_squared
  nonwinter_r[[i]] <- nonwinter_r_squared
}

cbind(predictors, winter_r, nonwinter_r)
```


*Adding potential interaction term for pop change*
```{r}
month_data <- month_data %>% mutate(high_growth = if_else(pop_change > 1, TRUE, FALSE))
winter_data <- month_data %>% filter(is_winter)
nonwinter_data <-  month_data %>% filter(!is_winter)
```

*Seeing if high-growth can help explain the variance more*
```{r}
winter_r <- list()
nonwinter_r <- list()
for(i in 1:length(predictors)) {
  predictor <- predictors[i]
  winter_model <- lm(monthly_avg_pm25 ~ get(predictor) + get(predictor):high_growth, winter_data)
  winter_r_squared <- summary(winter_model)$adj.r.squared
  
  nonwinter_model <- lm(monthly_avg_pm25 ~ get(predictor) + get(predictor):high_growth, nonwinter_data)
  nonwinter_r_squared <- summary(nonwinter_model)$adj.r.squared
  
  winter_r[[i]] <- winter_r_squared
  nonwinter_r[[i]] <- nonwinter_r_squared
}

cbind(predictors, winter_r, nonwinter_r)
```

*Seeing if can break it down month by month*
```{r}
monthly_statistics <- list()

for(i in 1:12) {
  single_month <- month_data %>% filter(month == i)
  
  predictor_rsquared <- list()

  for(j in 1:length(predictors)) {
    predictor <- predictors[j]
    model <- lm(monthly_avg_pm25 ~ get(predictor) + get(predictor):high_growth, single_month)
    r_squared <- summary(model)$adj.r.squared
    
    predictor_rsquared[[j]] <- r_squared
  }

  monthly_statistics[[i]] <- cbind(predictors, predictor_rsquared)
}

monthly_statistics

```

```{r}
month_data_with_predictions <- augment(ols, data = month_data)

month_data_with_predictions <- month_data_with_predictions %>% mutate(predicted = exp(.fitted))

# plot residuals
month_data_with_predictions %>% 
  ggplot(aes(x = .resid)) +
  geom_histogram(bins = 50) +
  geom_vline(xintercept=0) +
  ggtitle('Jan 2020')

summary(ols)
```


```{r}
month_data_with_predictions_geo <- st_as_sf(month_data_with_predictions, coords = c("lon", "lat"), crs = 4326) 
tm_shape(month_data_with_predictions_geo) + tm_dots(col='monthly_avg_pm25')
tm_shape(month_data_with_predictions_geo) + tm_dots(col='.fitted')
tm_shape(month_data_with_predictions_geo) + tm_dots(col='.resid')
```

