---
title: "Computing Summer LURS"
author: "Hayley Garment"
date: "7/7/2020"
output: html_document
---

In this file:
1. Join predictor and indpendent variables at each station
2. Regression

Output:


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(broom)
library(rgdal)
library(sp)
library(raster)
```

*Load predictor variables at each station*
```{r}
predictor_vals <- read.csv('data/sensor_locations_predictor_values_additional_vars.csv') %>% 
  rename(station_serial = serial_num) %>% dplyr::select(-FID, -lat, -lon)
```


*Load independent variable at each station -pm2.5 avg
**Sample**
```{r}
monthly_avg <- readRDS('data/monthly_avgs/month_of_2019-06-01.rds') %>% dplyr::select(-datetime) %>% filter(station_serial != 'SLSVLW4')
```

*look on map*
```{r}
tmap_mode("view")
monthly_geo <- st_as_sf(monthly_avg, coords = c("lon", "lat"), crs = 4326) 
tm_shape(monthly_geo) + tm_dots(col='monthly_avg_pm25')
```


**1. Join predictor and indpendent variables at each station**
```{r}
month_data <- left_join(monthly_avg, predictor_vals)

#month_data
```

**Looking at plots for avg pm25 vs predictors**
```{r}
if (false) {
ggplot(month_data, aes(x=dist_to_trunk_rd, y=monthly_avg_pm25)) + geom_point()
ggplot(month_data, aes(x=ub_pop_2019_1km, y=monthly_avg_pm25)) + geom_point()
ggplot(month_data, aes(x=ub_topogra, y=monthly_avg_pm25)) + geom_point()
ggplot(month_data, aes(x=stove_kernel_density_radius_007, y=monthly_avg_pm25)) + geom_point()


ggplot(month_data, aes(x=stove_conc_005, y=monthly_avg_pm25)) + 
  geom_point(col=month_data$district)
}
```


**2. Regression**


```{r}
predictors <- month_data %>% dplyr::select(-lon, -lat, -station_serial, -monthly_avg_pm25 , -district) %>% colnames()
```


```{r}
predictor_rsquared <- list()

for(i in 1:length(predictors)) {
  predictor <- predictors[i]
  model <- lm(monthly_avg_pm25 ~ get(predictor), month_data)
  r_squared <- summary(model)$adj.r.squared
  
  predictor_rsquared[[i]] <- r_squared
}

cbind(predictors, predictor_rsquared)

```


*Adding potential interaction term for pop change*
```{r}
month_data <- month_data %>% mutate(high_growth = if_else(pop_change > 1, TRUE, FALSE))
```

```{r}
predictor_rsquared <- list()

for(i in 1:length(predictors)) {
  predictor <- predictors[i]
  model <- lm(monthly_avg_pm25 ~ get(predictor):high_growth, month_data)
  r_squared <- summary(model)$adj.r.squared
  
  predictor_rsquared[[i]] <- r_squared
}

cbind(predictors, predictor_rsquared)

```

*trying to add the district as a categorical variable*
```{r}
month_data

ub_districts <-read_csv('data/ub_districts.csv') %>% 
  rename(district = OBJECTID) %>% 
  dplyr::select(district, Name)

month_data <- left_join(month_data, ub_districts) %>% rename(district_name = Name)
```


COMBINED MODEL FOR MONTHLY AVG
*Testing out variables together*
*Ok with stove_conc005:high growth + PathDis_ci + population!*
*0.41 for September*
*0.28 for july, with path + highgrowth:stove density_007*
*june: stove_conc_005 + high_growth:ub_pop_2019_1km: 0.25*
```{r}
ols <- lm(monthly_avg_pm25 ~ stove_conc_005 + high_growth:ub_pop_2019_1km, month_data)

ols %>% summary()

tidy(ols)
```




```{r}
month_data_with_predictions <- augment(ols, data = month_data)

month_data_with_predictions <- month_data_with_predictions %>% mutate(predicted = exp(.fitted))

# plot residuals
month_data_with_predictions %>% 
  ggplot(aes(x = .resid)) +
  geom_histogram(bins = 50) +
  geom_vline(xintercept=0) +
  ggtitle('Jan 2020')

summary(ols)
```


```{r}
month_data_with_predictions_geo <- st_as_sf(month_data_with_predictions, coords = c("lon", "lat"), crs = 4326) 
tm_shape(month_data_with_predictions_geo) + tm_dots(col='monthly_avg_pm25')
tm_shape(month_data_with_predictions_geo) + tm_dots(col='.fitted')
tm_shape(month_data_with_predictions_geo) + tm_dots(col='.resid')
```

