---
title: "Calculating Weekly and Monthly Averages"
author: "Hayley Garment"
date: "6/18/2020"
output: html_document
---

In this file:
1. Checking the time range for each sensor
2. Sorting out the MHPP97G station
3. Calculating Monthly Means of pm2.5 per station

Output:

1. data/start_end_date_by_sensor.rds - for each sensor earliest and latest sensor reading
2. data/sensor_data_tidy.rds - all data tidied, by averaging out the data for the MHPP97G station
3. data/sensor_means_by_month_over_650_readings.rds - only sensors with over 650 readings in given month


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)


library(tidyverse)
library(readr)
library(lubridate)
library(tmap)
library(sf)
library(mapview)
library(tmap)
library(broom)
library(rgdal)
```

*Fetch data*
```{r}
sensor_data <- readRDS('data/all_stations_pm25.rds')
```

*Change the date to be POSIXct*
```{r}
ub_timezone <- "Asia/Ulan_Bator"

sensor_data <- sensor_data %>% mutate(datetime = ymd_hms(datetime, tz = ub_timezone))
```

**1. Checking the time range for each sensor**

*Check the beginnings and endings of each sensor*
```{r}
start_end_date_by_sensor <- sensor_data %>% group_by(station_serial) %>% 
  summarize(earliest_date = min(datetime), latest_date = max(datetime)) %>% 
  ungroup() %>% 
  arrange(earliest_date)

saveRDS(start_end_date_by_sensor, 'data/start_end_date_by_sensor.rds')
```

*Look at readings over time*
```{r}
  # manually change and examine
  i <- 15
  code <- start_end_date_by_sensor$station_serial[[i]]
  
  sensor_data %>% filter(station_serial == code) %>%
    mutate(date = date(datetime)) %>% 
    ggplot(aes(x=date)) +
    geom_histogram(bins=100)
  
  # has to have over 672 hrs per month to considered for 'hourly avg for a month'
  # has to have 168 hrs to be week to be considered 'hourly average for a whole week'
  # 'monthly = over 650 readings, 'weekly' = over 160 readings

  # want over 95% of the values there to have the 'avg
```


**2. Sorting out the MHPP97G station**
```{r}
# This sensor must be newer, it only started outputting data Dec 24th of 2019, late last year!

mhp_data <- sensor_data %>% filter(station_serial == 'MHPP97G')
mhp_data %>% count()
mhp_data %>% head(1000) %>% ggplot(aes(x = datetime)) + geom_histogram()

# sometimes the sensor gets readings more than 4x per hour! why? how to do an avg per hour?

mhp_data <- mhp_data %>% mutate(date = date(datetime), hour = hour(datetime), minute = minute(datetime))

mhp_data %>% group_by(date, hour) %>% 
  summarize(num_readings = n()) %>% 
  ungroup() %>% filter(num_readings > 4) %>% 
  ggplot(aes(x = num_readings)) + 
  geom_histogram()

# does it matter if there are multiple readings per hour? how about per minute?


mhp_data %>% filter(date == '2020-02-04' & hour == 1) # seem to be duplicates in a single second

#Q: how many of the duplicates are same-second dupes? A: not all :(

mhp_data %>% group_by(date, hour, minute) %>%
  summarize(num_readings = n()) %>% 
  ungroup() %>% 
  group_by(date, hour) %>%
  summarize(num_readings = n()) %>% 
  ungroup() %>% 
  filter(num_readings > 4) %>% 
  ggplot(aes(x = num_readings)) + 
  geom_histogram()
```


```{r}
# Calculate hourly avg with duplicates and extra readings

second(mhp_data$datetime) <- 0

mhp_hourly_means <- mhp_data %>% group_by(date, hour) %>% 
  summarize(hourly_pm25 = mean(pm25_ug)) %>% 
  ungroup()

mhp_hourly_means <- mhp_hourly_means %>% mutate(datetime = ymd_h(paste(date, hour, sep='')))

mhp_hourly_means %>% ggplot(aes(x=datetime, y=hourly_pm25)) + geom_line()


# Calculate with no dupes - doesn't make much of a difference..

#mhp_no_dupes <- mhp_data[!duplicated(mhp_data$datetime),]

#mhp_hourly_means <- mhp_no_dupes %>% group_by(date, hour) %>% 
  summarize(hourly_pm25 = mean(pm25_ug)) %>% 
  ungroup()

#mhp_hourly_means <- mhp_hourly_means %>% mutate(datetime = ymd_h(paste(date, hour, sep='')))

#mhp_hourly_means %>% ggplot(aes(x=datetime, y=hourly_pm25)) + geom_line()

```

```{r}
sensor_data <- sensor_data %>% filter(station_serial != 'MHPP97G') # remove this data

#mhp_hourly_means %>% head()
mhp_hourly_means_tidied <- mhp_hourly_means %>% select(datetime, hourly_pm25) %>%
  mutate(station_serial = 'MHPP97G') %>% 
  rename(pm25_ug = hourly_pm25)

sensor_data %>% head()

sensor_data_tidy <- rbind(sensor_data, mhp_hourly_means_tidied)

sensor_data_tidy %>% distinct(station_serial) %>% count()
sensor_data %>% distinct(station_serial) %>% count()

sensor_data_tidy %>% filter(station_serial == 'MHPP97G')

saveRDS(sensor_data_tidy, 'data/sensor_data_tidy.rds')
```



**3. Calculating Monthly Means of pm2.5 per station**
*Group by Month*
```{r}
sensor_data_tidy <- readRDS('data/sensor_data_tidy.rds')

sensor_data_tidy_groupable <- sensor_data_tidy %>% 
  mutate(year = year(datetime), month = month(datetime))

sensor_means_by_month <- sensor_data_tidy_groupable %>% group_by(station_serial, year, month) %>% 
  summarize(num_readings = n(), monthly_avg_pm25 = mean(pm25_ug)) %>% 
  ungroup()
```


```{r}
reliable_sensors_per_month_650 <- sensor_means_by_month %>% group_by(year, month) %>% 
  summarize(num_stations_over_x = sum(num_readings>=650)) %>% 
  ungroup()

reliable_sensors_per_month_600 <- sensor_means_by_month %>% group_by(year, month) %>% 
  summarize(num_stations_over_x = sum(num_readings>=600)) %>% 
  ungroup()

reliable_sensors_per_month_550 <- sensor_means_by_month %>% group_by(year, month) %>% 
  summarize(num_stations_over_x = sum(num_readings>=550)) %>% 
  ungroup()

reliable_sensors_per_month_650 %>% mutate(datetime = ymd(paste(year, month, 1, sep='-'))) %>% 
  ggplot(aes(x=datetime)) +
  geom_col(aes(y=num_stations_over_x))

reliable_sensors_per_month_600 %>% mutate(datetime = ymd(paste(year, month, 1, sep='-'))) %>% 
  ggplot(aes(x=datetime)) +
  geom_col(aes(y=num_stations_over_x))

reliable_sensors_per_month_550 %>% mutate(datetime = ymd(paste(year, month, 1, sep='-'))) %>% 
  ggplot(aes(x=datetime)) +
  geom_col(aes(y=num_stations_over_x))
# so only a few reliable sensors per month, and not 29 like i'd hope, more like 15 - sad :(
```

*Saving sensor means by month*
```{r}
useable_sensor_means_by_month <- sensor_means_by_month %>% filter(num_readings >= 650) %>% mutate(datetime = ymd(paste(year, month, 1, sep='-')))
saveRDS(useable_sensor_means_by_month, 'data/sensor_means_by_month_over_650_readings.rds')
```
